\section{Experimental Setup}
\label{sec:setup}

\subsection{Data}
\label{ssec:data}
The corpus consists of \(1{,}500\) real PubMed abstracts streamed from
\texttt{ncbi/pubmed} and \(1{,}500\) BioMistral-7B zero-shot fakes
generated from biomedical topic stubs. The combined \(3{,}000\) abstracts
are stratified-split \(80/10/10\) into Train (\(2{,}400\)), Val
(\(300\)), and Test (\(300\)), each balanced \(1\!:\!1\) real-to-fake.
Per-round fake pools (\(K=250\)) are sampled \emph{outside} the train/val/
test splits and never re-enter them; this keeps the test set untouched
across all rounds and conditions. The full data manifest, including
per-row hashes, is committed to the repository so that any reviewer can
verify there is no train--test contamination.

\subsection{Conditions (the four-cell ablation)}
\label{ssec:conditions}
Table~\ref{tab:conditions} maps each condition onto the components of
Algorithm~\ref{alg:loop}.

\begin{table}[t]
\caption{Four-condition ablation. The only experimental variable is which
components of the adversarial loop are enabled.}
\label{tab:conditions}
\centering
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{@{}llccc@{}}
\toprule
& \textbf{Generator} & \textbf{Agent} & \textbf{Retrain} & \textbf{Rounds} \\
\midrule
\textbf{A} static\_baseline & BioMistral & --- & no  & --- \\
\textbf{B} seqgan\_only     & SeqGAN     & --- & yes & 3 \\
\textbf{C} agent\_only      & BioMistral & Qwen2.5 & no  & 3 (gen+rewrite) \\
\textbf{D} full\_pipeline   & BioMistral & Qwen2.5 & yes & 3 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Cross-domain Probe: RAID}
\label{ssec:raid}
We evaluate Condition~A's detector (without retraining) on the biomedical
slice of the RAID benchmark \cite{dugan2024raid}: \(200\) samples
(\(19\) real, \(181\) fake) with fakes generated by ChatGPT, GPT-4,
Claude, Llama, and other LLMs that the detector never saw. RAID is
strictly an evaluation set; no RAID samples enter training.

\subsection{Metrics}
\label{ssec:metrics}
We report four metrics, all computed on the held-out Test set unless
explicitly tagged ``fake-pool'':

\begin{itemize}[leftmargin=*]
\item \textbf{AUC.} Area under the ROC curve. Threshold-free.
\item \textbf{F1.} Harmonic mean of precision and recall at threshold
  \(0.5\).
\item \textbf{Accuracy.} Fraction of correct labels.
\item \textbf{Evasion rate.} Fraction of \emph{fake} samples assigned
  probability $< 0.5$ (i.e., labelled as real). Computed both on the
  Test set's \(150\) fakes and on each round's \(250\)-sample
  \emph{fake-pool}. The fake-pool evasion is the metric the loop is
  effectively optimising against.
\end{itemize}

\textbf{Confidence intervals.} All test-set rates are reported with Wilson
\(95\%\) confidence intervals. At \(n=300\) the half-width is
\(\pm 0.029\); at \(n=250\) (per-round fake pool) it is \(\pm 0.062\).
We will use these CIs to bound any per-round claims.

\subsection{Hardware and Software}
\label{ssec:hardware}
All experiments run on a single Apple~M3~Max~64\,GB laptop using
PyTorch~2.4 with the Apple~MPS backend and bf16 mixed precision. We set
\texttt{PYTORCH\_MPS\_HIGH\_WATERMARK\_RATIO=0.0} and
\texttt{OMP\_NUM\_THREADS=10}. The orchestrator process is wrapped in
\texttt{caffeinate -dims -w \$PID} so the lid can close without
suspending the run.

\subsection{Wall-clock Budget}
\label{ssec:walltime}
Table~\ref{tab:walltime} reports the wall-clock breakdown of one
end-to-end run (\(10\,\mathrm{h}\,01\,\mathrm{m}\)) and where the time
goes. Data preparation (initial \(1{,}500\)-fake BioMistral generation)
and Condition~D dominate; plots, RAID, and the M4 skip are essentially
free.

\begin{table}[t]
\caption{End-to-end wall-clock on a single Apple M3 Max
(bf16, MPS). The whole pipeline is one shell script.}
\label{tab:walltime}
\centering
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{@{}lrr@{}}
\toprule
\textbf{Stage} & \textbf{Wall-clock} & \textbf{\%} \\
\midrule
Data prep (1{,}500 PubMed + 1{,}500 BioMistral)
                                & 3\,h\,55\,m & 39 \\
Condition A (baseline detector) & 13\,m       &  2 \\
Condition B (SeqGAN $\times$ 3 rounds)
                                & 56\,m       &  9 \\
Condition C (BioMistral + Qwen $\times$ 3)
                                & 2\,h\,05\,m & 21 \\
Condition D (B+C, with retrain $\times$ 3)
                                & 2\,h\,52\,m & 29 \\
Plots                           & 0\,s        & 0 \\
RAID benchmark                  & 22\,s       & $<$ 1 \\
M4 (skipped, dataset removed)   & 2\,s        & $<$ 1 \\
\midrule
\textbf{Total}                  & \textbf{10\,h\,01\,m} & 100 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{What We Did Not Run}
For honesty: the M4 \cite{wang2024m4} cross-domain benchmark was removed
from the Hugging~Face Hub between project start and this run. We record a
graceful skip in \texttt{condition\_D\_m4\_metrics.json}. A
Llama-3.2-3B transfer-attack evaluation is queued but not in this draft;
the empty \texttt{transfer\_test.csv} placeholder is committed.
