\section{Limitations and Future Work}
\label{sec:limitations}

We catalogue limitations explicitly so reviewers and downstream users can
calibrate the results.

\subsection{Limitations}

\paragraph{Single random seed per run.}
All four conditions and the RAID probe were evaluated under
\texttt{base=42} with per-round \texttt{set\_seed(42 + r)}. The
\(\pm 0.029\) Wilson half-width on test \(n=300\) bounds within-run
variance, but does not bound run-to-run variance from re-seeding.
Reported numbers should be read as point estimates; multi-seed
replication is required for any confidence-interval claim across
runs.

\paragraph{Three-thousand-sample scale.}
Test \(n=300\) produces a \(\pm 0.029\) CI half-width — wide enough that
the C\,$=$\,A and D\,$=$\,A equivalences are formally ``not significantly
different,'' rather than proven equal. A paper-grade replication should
push to \(n=2{,}000\) (Wilson half-width \(\pm 0.011\)) before treating
the C\,$=$\,D pathology claim as a tight finding.

\paragraph{Single biomedical domain.}
The detector is trained on PubMed and one biomedical-specialised LLM. We
do not test on clinical notes (MIMIC-III, MIMIC-IV) or on biomedical
preprints (bioRxiv, medRxiv). The cross-domain failure on RAID is
suggestive but RAID itself is heterogeneous; a within-biomedical
domain-shift study (PubMed-trained, MIMIC-tested) would tighten the
domain-shift claim.

\paragraph{Zero-shot generator and agent.}
Both BioMistral-7B (the generator) and Qwen2.5-7B (the agent) are used
zero-shot. A LoRA-fine-tuned version of either, trained against the
detector's logits, would likely change the picture. We treat this as
the most important pre-paper engineering investment
(Section~\ref{ssec:future}).

\paragraph{Best-validation-AUC checkpoint selection.}
The C\,$=$\,D pathology is downstream of this design choice. We implement
an adversarial-aware selector (\texttt{--checkpoint\_selector adversarial}
in \texttt{training/adversarial\_loop.py}) that promotes the epoch with the
lowest fake-pool evasion rather than highest val-AUC
(Section~\ref{ssec:ckpt_adv}). A quantitative comparison of
selectors — sweeping best-pool-evasion, worst-case evasion across pools, and
average over the last $k$ epochs — remains future work.

\paragraph{No human evaluation.}
We do not include a blinded human reader study in this draft. Reviewers
will reasonably want one; we plan a 50-sample blinded protocol
(Section~\ref{ssec:future}).

\paragraph{M4 cross-domain benchmark unavailable.}
The \texttt{Chardonneret/M4} dataset \cite{wang2024m4} was removed from
the Hugging~Face Hub between project start and this run. We log a
graceful skip in \texttt{condition\_D\_m4\_metrics.json} and propose
\texttt{Hello-SimpleAI/HC3} \cite{guo2023hc3} or
\texttt{yaful/MAGE} \cite{li2024mage} as replacements for the paper
revision.

\paragraph{Multi-family training pending full-scale run.}
Condition~E (\texttt{models/detector/train\_multi\_family.py}) trains
on a BioMistral~+~SeqGAN~+~Llama mixed corpus and is designed to
compress the \(\sim\!140\times\) evasion spread. The implementation is
complete; full-scale \(3\)k results are not yet available. A
Llama-3.2-3B-only transfer attack (the $2\times 2$ family-cross-check matrix)
is the highest-priority missing experiment for the next revision.

\paragraph{Post-hoc calibration deployed but not yet evaluated at scale.}
Temperature scaling (\texttt{evaluation/calibration.py}) is implemented and
applies to Condition~A's detector on the RAID probe. The calibrated threshold
\(\theta^*\) is expected to close the AUC--accuracy gap
(Section~\ref{ssec:calibration_fix}), but a full quantitative comparison
with the uncalibrated baseline requires a held-out calibration split that
is not included in the current \(3\)k corpus.

\subsection{Future Work}
\label{ssec:future}

\paragraph{Pre-paper, this quarter.}
\begin{enumerate}[leftmargin=*]
\item \emph{Multi-seed replication.} Repeat the
  \(3{,}000\)-sample run under three additional seeds
  (\texttt{base} $\in \{43, 44, 45\}$) and report mean $\pm$ s.d.\
  rather than point estimates.
\item \emph{LoRA-hardened BioMistral.} Fine-tune BioMistral with DPO
  using the detector's real-probability score as the negative reward.
  Expected to break the validation-AUC ceiling and reactivate the
  retraining gradient.
\item \emph{Adversarial-aware checkpoint selector — re-run.}
  \texttt{--checkpoint\_selector adversarial} is implemented
  (Section~\ref{ssec:ckpt_adv}). The immediate priority is to re-run
  Conditions~B and~D end to end with the new selector and report
  whether the C\,$=$\,D pathology quantitatively dissolves.
\item \emph{Condition~E full-scale run.} Run
  \texttt{train\_multi\_family.py} at \(3\)k scale; report the complete
  $3\times 3$ evasion matrix (BioMistral, Llama, SeqGAN) for Conditions
  A and E; confirm the predicted evasion-spread compression.
\item \emph{Calibration evaluation.} Evaluate
  \texttt{evaluation/calibration.py} with a held-out calibration split;
  report pre- and post-calibration accuracy on RAID and quantify the
  AUC--accuracy gap closure.
\item \emph{Blinded human evaluation.} \(50\) abstracts (\(25\)
  real + \(25\) BioMistral fake), \(3\) M.Tech-level domain readers,
  per-reader and aggregated accuracy with Cohen's $\kappa$.
\end{enumerate}

\paragraph{Paper Tier~1 (peer-review defensible).}
Increase scale to \(2{,}000\) real + \(2{,}000\) fake, \(3\) rounds
$\times$ \(500\) per pool, test \(n=400\) (\(\pm 2.5\%\) CI). Wall-clock
budget on M3~Max: $\sim$\(16\) hours (one overnight). With batched
BioMistral generation (\texttt{batch\_size=4} in
\texttt{train\_generator.py}) we estimate
\(10\!-\!12\) hours.

\paragraph{Paper Tier~2 (reviewer-proof).}
Scale to \(10{,}000\) real + \(10{,}000\) fake, \(5\) rounds $\times$
\(1{,}000\) per pool, test \(n=2{,}000\) (\(\pm 1.1\%\) CI), full
family-cross-check matrix and human eval. Estimated wall-clock with
batching: $\sim$\(40\!-\!65\) hours.

\paragraph{Beyond the current pipeline.}
Two longer-horizon directions are worth flagging. (i)~A multi-domain
detector trained jointly on PubMed, MIMIC, and bioRxiv with
domain-adversarial pretraining \cite{ganin2016dann} should help with
cross-domain calibration. (ii)~A multi-family training corpus including
SeqGAN-style fakes, BioMistral fakes, and at least one general-purpose
LLM family (Llama, GPT) would convert the family-disclosure
recommendation in Section~\ref{ssec:family_disc} from a measurement
into a deployable defence.
