% =============================================================================
% BioShield — IEEE Conference Paper (first draft)
%
% Title: BioShield: A Negative Result on Adversarial Retraining for Biomedical
%        AI-Text Detection Under Generator-Family Shift
%
% Author: Venkata Rayudu Alapati  (M.Tech AI/ML, AP25122040029)
% Date  : April 2026
% =============================================================================
\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{array}
\usepackage{enumitem}
\usepackage{caption}
\usepackage{siunitx}
\usepackage{url}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!black,
  citecolor=blue!50!black,
  urlcolor=blue!50!black
}

\graphicspath{{figures/}}

\begin{document}

\title{BioShield: A Negative Result on Adversarial Retraining for Biomedical AI-Text Detection Under Generator-Family Shift}

\author{
\IEEEauthorblockN{Venkata Rayudu Alapati}
\IEEEauthorblockA{
\textit{M.Tech, Dept.\ of Computer Science and Engineering}\\
\textit{SRM University AP}\\
Andhra Pradesh, India \\
AP25122040029 \\
alapativenkatarayudu@gmail.com}
}

\maketitle

\begin{abstract}
We study whether a 3-round adversarial retraining loop can harden a biomedical
text deepfake detector against AI-generated abstracts. Our pipeline combines
(i)~a BiomedBERT-Large detector, (ii)~a BioMistral-7B zero-shot generator and a
SeqGAN baseline, and (iii)~a Qwen2.5-7B rewriting agent that targets the
top-25\% hardest fakes per round. We evaluate four conditions in a controlled
ablation on \(1{,}500\) real PubMed abstracts and \(1{,}500\) BioMistral fakes
(test \(n=300\), Wilson 95\% CI \(\pm 2.9\) percentage points), plus a RAID
cross-domain probe. Three findings emerge. \textbf{First}, generator-family
identity dominates evasion behaviour: SeqGAN fakes evade at \(98.7\%\),
BioMistral fakes at \(0.7\%\), and RAID's mixed-LLM corpus at \(98.3\%\) — a
roughly \(100\times\) spread on the same detector. \textbf{Second}, three
rounds of adversarial retraining did not measurably help at this scale:
condition~B's evasion stayed flat (\(0.993 \to 0.980 \to 0.987\), within Monte
Carlo noise on \(n=250\)), and conditions~C and~D produced byte-identical
metrics because best-validation-AUC checkpointing rolled back to the round-0
baseline (validation AUC ceiling \(0.9990\) was unreachable by retraining).
\textbf{Third}, the detector did not transfer cross-domain (RAID accuracy
\(0.11\), evasion \(0.983\)). We argue that (a)~published biomedical detectors
must disclose the generator family they were trained against, (b)~best-val-AUC
checkpoint selection silently hides retraining signal when the baseline is
already at ceiling, and (c)~a previously reported \(0.74 \to 0.54\) evasion
curve at \(500\)-sample scale was likely small-sample noise that did not
reproduce at \(3\)k. We position BioShield as a biomedical specialist and
treat the negative results as the paper's primary contribution.
\end{abstract}

\begin{IEEEkeywords}
AI-generated text detection, biomedical NLP, adversarial training,
SeqGAN, large language model rewriting agents, domain generalization,
BiomedBERT, negative results, reproducibility.
\end{IEEEkeywords}

\input{sections/01_introduction}
\input{sections/02_related_work}
\input{sections/03_method}
\input{sections/04_experimental_setup}
\input{sections/05_results}
\input{sections/06_discussion}
\input{sections/07_limitations_future_work}
\input{sections/08_conclusion}

\section*{Reproducibility Statement}
All code, configuration files, per-round metric JSONs, plots, and the
\(3{,}000\)-sample data manifest are released at
\url{https://github.com/Rayudualapati-25/BioShield}. The complete
\(10\,\mathrm{h}\,01\,\mathrm{m}\) pipeline reproduces with
\texttt{bash scripts/run\_presentation.sh} on a single Apple~M3~Max~64\,GB
machine. Random seeds (\texttt{base=42}, per-round
\texttt{set\_seed(42+r)}), bf16 dtype, and the
\texttt{microsoft/BiomedNLP-BiomedBERT-large} checkpoint are fixed across
conditions; the only variable is training data.

\section*{Acknowledgment}
The author thanks the maintainers of the BioMistral, BiomedBERT, Qwen, and
SeqGAN projects for releasing their models and code, and the Hugging~Face Hub
team for streaming PubMed access. The RAID benchmark
\cite{dugan2024raid} provided the cross-domain probe that anchors our
domain-shift analysis.

\bibliographystyle{IEEEtran}
\bibliography{refs}

\end{document}
